agdarsec -- Total Parser Combinators

### 2017-10-26 doc/paper/main.tex
[ doc ] adding an abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\end{abstract}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Parser combinator libraries represent parsers as functions and,
using higher-order functions, define a DSL of combinators allowing
users to quickly put together programs capable of handling complex
grammars. When moving to total functional languages such as Agda,
these programs cannot be directly ported: there is nothing in the
original definitions guaranteeing termination.

In this paper, we will introduce a 'guarded' modal operator acting
on types and show how it allows us to give more precise types to
existing combinators thus guaranteeing totality. The resulting
library is available online together with various usage examples
at \url{https://github.com/gallais/agdarsec}.
\end{abstract}
